### 2022-05-26 main/chapter_2ljets.tex
begin jets and btagging

@@

Although jet and $\met$ triggers were not studied in detail, they require
hard objects: examples are approximately $\ptjone > 400~\eV[G]$,
$p_\mathrm{T}^{\,j_3} > 200~\eV[G]$, or
$\met > 100~\eV[G]$~\cite{atlas_twiki_lowest_unprescaled}.
Leptons, however, are striking signals which are produced as smaller background
rates, as they suppressed by electroweak couplings.
Therefore, \atlas\ can trigger on leptons with much softer requirements;
lepton triggers allow us to use softer jets and $\met$, which are relied upon
throughout the $\twoljets$ analyses.

@@

\subsubsection{$b$-tagging}
\label{sec:btagging}

>>>>

\TODO{reference for trigger details, eta range?}

@@

Although jet and $\met$ triggers were not studied in detail, they can be
quickly ruled out since they hard objects: examples of these triggers require
approximately $\ptjone > 400~\eV[G]$, $p_\mathrm{T}^{\,j_3} > 200~\eV[G]$, or
$\met > 100~\eV[G]$~\cite{atlas_twiki_lowest_unprescaled}.
Leptons, however, are striking signals which are produced as smaller background
rates, as they suppressed by electroweak couplings.
Therefore, \atlas\ can trigger on leptons with much softer requirements;
lepton triggers allow us to use softer jets and $\met$, which are relied upon
throughout the $\twoljets$ analyses.

@@

Like leptons, jets are identified with `baseline' and `signal' requirements
with increasingly tight requirements on quality metrics and kinematics.

\TODO{anti-kt 0.4}

Baseline jets require $\pt > 20~\eV[G]$, and signal jets require
$\pt > 30~\eV[G]$.
The $\twoljets$ electroweak analysis uses only signal jets unless those jets
are $b$-tagged.

\subsubsection{$b$-tagging}
\label{sec:btagging}
Tagging adds additional labels to jets, and is particularly useful for
encoding flavour information derived from data within the jet cluster.
In particular, $b$-tagging attempts to identify jets originating from $b$
quarks, which have distinct features due to the long lifetimes and decay
channels of $B$ hadrons.

\TODO{context: charm quarks, large radius (jumbo) jets top higgs}
